
%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

\documentclass[10pt,a4paper,ragged2e]{maltacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the font if you want to
% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% \usepackage[default]{lato}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif

\usepackage{setspace}

\usepackage{mathpazo}
\usepackage{textcomp}
\usepackage{multicol}

% Color schemes:
% raisinblack_flame
% darkpurple_princetonorange
% blue_claret
% eerieblack_eggplant
% outerspace_forestgreen   
% raisinblack_midnightgreen
% teal_brown
% indigo
% blue
% violet
% you can set your custom colors with:
% \definecolor{AccentBody}{HTML}{002642}
% \definecolor{Primary}{HTML}{840032}
% \colorlet{primary}{Primary}
% \colorlet{accent_body}{AccentBody}

% this is my favourite but change it as you like
\setcolorscheme{eerieblack_eggplant}
\setlength\multicolsep{0pt}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}

%% sample.bib contains your publications
%% NOT SUPPORTED YET
% \addbibresource{sample.bib}

\name{Shubham Dwived}
\firstname{Shubham}
\familyname{Dwivedi}

\begin{document}
\tagline{Full Stack Developer}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{shubham00d@gmail.com}
  % \birthday{25\textsuperscript{th} Dec 0}
  % \homepage{www.homepage.com/}
  % \twitter{@twitterhandle}
  \linkedin{shubhamdwivedi27}
  \github{shubhamdwivedii}
  \location{New Delhi, India}
  \phone{+919599428859}
  % \mailaddress{lorem ipsum, dolor, sit, AM, 57846}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
  % \orcid{orcid.org/0000-0000-0000-0000}
}

\bio{3 years of experience solving engineering problems. 2+ years of experience writing JavaScript code in production. Deft at reverse engineering. Adept at writing testable, modular and simple code.}

\makecvheader

\cvsection{Experience}

\cvexperience{Full Stack Developer}{Codalien Technologies Pvt. Ltd.}{Feb 2019 -- Present}{New Delhi, DL, India}{JavaScript ES6, ReactJS, NodeJS, Express, React Native, Redux, VueJS, MongoDB, GraphQL}
\begin{itemize}
  % \item Worked on various web and mobile applications powered by latest frontend technologies.
  \item Developed both frontend (web and mobile) applications as well as backend services powered by latest web technologies and frameworks.
  \item Modelled and assisted designing of database structures for projects such as TravX (MongoDB), Proximity.io (Firestore). Overcame various design challenges such as implementing DB support for custom vouchers (for TravX) with support for subitmes and dynamic field types. 
  \item Maintained a unified codebase for multiplatform applications such as Toyfull (ReactJS, Cordova), Drata(VueJS, ElectronJS) and TravX(VueJS, Cordova).
  \item Created various dynamic components with reusability in mind (such as a reusable Table Group with support for server-side pagination, filtering and sorting) for data/info centric applications such as Perspectico.AI (ReactJS) and 1UPVision VMS (ReactJS)
  \item Created a dynamic form builder for 1UPVision VMS where user can drag-n-drop form elements from toolbar (react-dnd) and rearrange then on a grid (react-grid-layout) to create custom forms for visitors.
  \item Worked on various native mobile applications powered by React-Native such as Proximity.io, Evermee, Credbo, LeapSkills and Novartis. 
  \item Designed and implemented data flow and store management using Redux(with Thunk and Saga), VueEx and MobX throughout various frontend applications.
  \item Utilized various UI component libraries such as AntD, MaterialUI, Buefy(Bulma), Bootstrap, Native-Base etc. to achieve a clean and professional look for applications. 
  \item Worked closely with the UI designers to implement custom designs according to various client's requirements.
  \item Developed and integrated various REST API and GraphQL services in both backend and frontend side.
  \item Worked with services such as Twilio, Cloudinary, Stripe, Auth0, Firebase, S3, Google APIs etc. to implement features such at video/text chat (Proximity.io), image/data storage (Evermee, Credbo), payment integration, calendar implementation, location services and authentication.  
  \item Assisted and lead development of admin panels and content management systems powered by KeystoneJS (Node, GraphQL, React).
\end{itemize}

\divider

\cvexperience{Software Development Intern}{DataGrokr Analytics Pvt. Ltd.}{Jun 2017 - Dec 2017}{Bengaluru, KA, India}{Python, Angular, AWS, CloudFormation, EC2, S3, Lambda, DynamoDB, Linux}
\begin{itemize}
  \item Worked independently as well as assisted senior developers in various coding and testing functions. 
  \item Worked on several DevOps technologies including AWS Cloud Services (EC2, S3, Route 53, CloudFormation, API Gateway, Lambda, DynamoDB etc.), Python, Shell scripting and Chef. 
  \item Developed various Python based tools using AWS Boto3 SDK to perform various tasks such as using CloudFormation templates to launch EC2 instances, backing up AMIs and performing other DevOps tasks. 
  \item Also built serverless web applications using Angular 2 with back-end REST API powered by python scripts running in AWS lambda service.
\end{itemize}

\divider
\medskip

\cvsection{Education}
\medskip
\begin{multicols}{3}

  \cvuniversity{B.Tech. (CSE)}{Inderprastha Engg. College (AKTU)}{2017}{Ghaziabad, UP}% last param is location

  % this helps if columns are not the same
  \vfill\null
  \columnbreak

  \cvuniversity{XIIth (CBSE)}{Tagore Sr. Sec. School}{ 2012 }{Mayapuri, Delhi}{}

  \vfill\null
  \columnbreak

  \cvuniversity{Xth (CBSE)}{N.C. Jindal Public School}{ 2010 }{Punjabi Bagh, Delhi}{}
  \vfill\null
  \columnbreak

\end{multicols}

\medskip

% \cvsection{Technical Skills}
% \medskip
% \cvsubsection{Programming}
% \smallskip
%   \begin{multicols}{5} % adjust #cols as needed
%     \cvlistitem{Python}{}
%     \cvlistitem{JavaScript ES6}{}
%     \cvlistitem{Lua}{}
%     \cvlistitem{TypeScript}{}
%     \cvlistitem{C\#}{}
%   \end{multicols}
% \medskip

% \cvsubsection{{Frameworks}}
% \smallskip
%   \begin{multicols}{5} % adjust #cols as needed
%     \cvlistitem{ReactJS}{}
%     \cvlistitem{Redux}{}
%     \cvlistitem{NodeJS}{}
%     \cvlistitem{VueJS}{}
%     \cvlistitem{React Native}{}
%     \cvlistitem{KeystoneJS}{}
%     \cvlistitem{Express}{}
%     \cvlistitem{GraphQL}{}
%     \cvlistitem{ElectronJS}{}
%   \end{multicols}
% \medskip

% \cvsubsection{{Tools and Databases}}
% \smallskip
%   \begin{multicols}{5} % adjust #cols as needed
%     \cvlistitem{MongoDB}{}
%     \cvlistitem{Linux}{}
%     \cvlistitem{AWS}{}
%     \cvlistitem{Git}{}
%     \cvlistitem{DynamoDB}{}
%     \cvlistitem{Firestore}{}
%     \cvlistitem{Firebase}{}
%   \end{multicols}
% \medskip

% \divider

% \cvsubsection{Other Activities and Projects}
% \medskip
% \begin{multicols}{3}
%   \cvlistitem{Pizza maker}{from 2014 -- 100+ pizzas}  
%   \cvlistitem{Computer Club}{from 2016 -- Senior Member}  
%   \cvlistitem{Big brother}{from 2005 -- experience with children}
%   \cvlistitem{Semester project}{Spring 2020 -- School project}
%   \cvlistitem{Built another volcano}{Fall 2019 -- School project}
%   \cvlistitem{Built a volcano}{Winter 2018 -- Science fair project}
% \end{multicols}

% \medskip

\cvsection{Interests}
% \medskip

\begin{multicols}{4} % adjust cols as needed
  \cvlistitem{Golang}{Currently learning}
  % \columnbreak
  
  \cvlistitem{Music}{Linkin Park, Radiohead, Coldplay, The Strokes}
  % \columnbreak

  % \cvlistitem{Exploring Places}{Trave}
  % \columnbreak


  \cvlistitem{Lua Programming}{For Game Development}
  % \columnbreak

  \cvlistitem{Video Games}{CS:GO, Valorant, Biohazard}
  % \columnbreak
  
\end{multicols}

% try to keep it on one page only !

% \cvsection{Why Me?}
% \begin{itemize}
%   \item I approach solutions with ”How can it fail” and ”What if it fails” mindset.
%   \item Skillful in profiling and optimizing code. 
%   \item Really good at finding patterns and relations. 
%   \item Proficient in developing microservices and modules.
%   \item Good grasp on programming fundamentals including OOP, Data Structures and Algorithms.
%   \item I see failures as a path to success and knowledge.
%   \item I keep my pride and ego aside to create room for improvement and learning.
%   \item I strive for simplicity and I don’t confuse simple with easy.
%   \item When necessary, I am willing to unlearn what I know and start over.
%   \item A believer in creating habits and consistency.
%   \item I understand that not everyone is the same. People can have completely different opinions.
% \end{itemize}


\end{document}
